Increasing Performance via Gamification in a Volunteer-Based Evolutionary Computation System

### 2017-11-10 2017-EUROPAR/Gamification/paper.tex
Deleted typo

This trade-off between ease of use, allowing users to
participate by just visiting a web page, and personalization, making
registration compulsory and subsequently authenticate in order to
participate, is what we will analyze in this paper. In a sociotechnical system such as this one, every
decision the user has to take has an influence on the overall
performance, and registration could be seen as a hurdle to volunteers
trying to participate in an ephemeral experiment, so it is a challenge
to analyze what actually happens in this case; quite clearly, the
inclusion of gamification techniques has an impact on page loading and
complexity of server-side programming; if eigher the number of users
or the amount of time they contribute to the experiment is not enough,
it would be better to revert to the purely anonymous system.

>>>>

This trade-off between ease of use, allowing users to
participate by just visiting a web page, and personalization, making
registration compulsory and subsequently authenticate in order to
participate, is what we will analyze in this paper. In a sociotechnical system such as this one, every
decision the user has to take has an influence on the overall
performance, and registration could be seen as a hurdle to volunteers
trying to participate in an ephemeral experiment, so it is a challenge
to analyze what actually happens in this case; quite clearly, the
inclusion of gamification techniques has an impact on page loading and
complexity of server-side programming; if the number of users
or the amount of time they contribute to the experiment is not enough,
it would be better to revert to the purely anonymous system.
